Supplementary Materials- A Bayesian approach to burial networks to infer social changes in northeastern Taiwan during the European colonization period

### 2021-02-19 analysis/paper/supplementary-material.Rmd
edit the main text in paper rmd
add a table to SI

<!-- burial data and the definition of tie formation: partially move to SI  -->
For trade beads with substantial differences in quantities between burials, we described each burial as having one of four levels according to their distributions across all burials (Figure \@ref(fig:figure-raincloud-beads)). Gold-foil beads are in levels of high (\>3), upper-middle (3), lower-middle (2), and low (1); carnelian beads are in levels of high (\>6), upper-middle (4-6), lower-middle (3), and low (1-2); glass beads are in levels of high (\>6), upper-middle (3-6), lower-middle (2), and low (1). If burial 1 and burial 2 both have high quantities of agate beads, then there will be a tie connecting them. For burial attributes, we assigned burials to different groups according to their age, sex, burial value and the presence/absence of ritual pottery. We have three groups for the age attribute, 0-12, 12-20, and above 20; two groups for the sex attribute, male and female, and four groups for the burial value that are specified in the main paper document.

```{r raincloud-beads, fig.cap = "The distributions of different types of trade beads across all burials analyzed in this paper."}
# combine ridge plots 1 & 4 in the 000-prep-data file
library(tidyverse)
library(ggridges)
ridge_1_and_4 <-
  burial_beads %>%
  mutate(type = case_when(
    type == "Golden_bead" ~"gold-foil bead",
    type == "all_glass_bead" ~"glass bead",
    type == "Agate_bead" ~"carnelian bead")) %>% 
  ggplot(aes(x = value,
             y = type,
             fill = factor(stat(quantile)))) +
  stat_density_ridges(
    geom = "density_ridges_gradient",
    calc_ecdf = TRUE,
    quantiles = 4,
    quantile_lines = TRUE,
    jittered_points = TRUE,
    alpha = 0.7,
    vline_size = 0.5,
    vline_color = "grey10",
    point_size = 2.5,
    point_alpha = 0.4,
    position = position_raincloud(adjust_vlines = TRUE),
    rel_min_height = 0.01,
    scale = 0.5, # so the filled regions don't overlap on the points
    size = 0.2) +
  scale_x_continuous(limits = c(1, 15),
                     expand = c(0.1, 0)) +
  scale_fill_viridis_d(name = "Quartiles") +
  theme_minimal()

@@

>>>>

<!-- burial data and the definition of tie formation: partially move to SI  -->
For trade beads with substantial differences in quantities between burials, we described each burial as having one of four levels according to their distributions across all burials (Figure \@ref(fig:figure-raincloud-beads)). Gold-foil beads are in levels of high (\>3), upper-middle (3), lower-middle (2), and low (1); carnelian beads are in levels of high (\>6), upper-middle (4-6), lower-middle (3), and low (1-2); glass beads are in levels of high (\>6), upper-middle (3-6), lower-middle (2), and low (1). If burial 1 and burial 2 both have high quantities of agate beads, then there will be a tie connecting them. For burial attributes, we assigned burials to different groups according to their age, sex, burial value and the presence/absence of ritual pottery. We have three groups for the age attribute, 0-12, 12-20, and above 20; two groups for the sex attribute, male and female; and four groups for the burial value that are specified in the main paper document. Table \@ref(tab:age-sex-table) shows the number of burials, of which sex and age can be determined.

```{r raincloud-beads, fig.cap = "The distributions of different types of trade beads across all burials analyzed in this paper."}
# combine ridge plots 1 & 4 in the 000-prep-data file
library(ggridges)
ridge_1_and_4 <-
  burial_beads %>%
  mutate(type = case_when(
    type == "Golden_bead" ~"gold-foil bead",
    type == "all_glass_bead" ~"glass bead",
    type == "Agate_bead" ~"carnelian bead")) %>% 
  ggplot(aes(x = value,
             y = type,
             fill = factor(stat(quantile)))) +
  stat_density_ridges(
    geom = "density_ridges_gradient",
    calc_ecdf = TRUE,
    quantiles = 4,
    quantile_lines = TRUE,
    jittered_points = TRUE,
    alpha = 0.7,
    vline_size = 0.5,
    vline_color = "grey10",
    point_size = 2.5,
    point_alpha = 0.4,
    position = position_raincloud(adjust_vlines = TRUE),
    rel_min_height = 0.01,
    scale = 0.5, # so the filled regions don't overlap on the points
    size = 0.2) +
  scale_x_continuous(limits = c(1, 15),
                     expand = c(0.1, 0)) +
  scale_fill_viridis_d(name = "Quartiles") +
  theme_minimal()

@@

```{r age-sex-table}
library(tidyverse)
library(flextable)
age_sex_by_phase <-
  burial_three_period_age_tidy %>% 
  select(Age_scale, gender, Phase) %>% 
  group_by(Phase, gender, Age_scale) %>% 
  filter(!Phase %in% c("disturbed", "chi")) %>% 
  count() %>% 
  pivot_wider(names_from = c(Phase, gender), 
              values_from = n) %>% 
  mutate(Age_scale = factor(Age_scale,
                            levels = c("0-12", "12-20", "+20", "NA"))) %>% 
  arrange(Age_scale) %>% 
  rename(age = Age_scale) %>% 
  select(age, pre_male, pre_female, pre_NA, post_male, post_female, post_NA)

ft_age_sex <- flextable(age_sex_by_phase) %>% 
  set_header_labels(pre_male = "pre-European", pre_female = "pre-European",
                    pre_NA = "pre-European", post_male = "post-European", 
                    post_female ="post-European", post_NA = "post-European") %>%
  merge_at(i = 1, j = 2:4, part = "header") %>% 
  merge_at(i = 1, j = 5:7, part = "header") %>% 
  add_header_row(values = c("","male", "female", "NA", 
                            "male", "female", "NA"), top = FALSE) %>% 
  align(j = 2:7, align = "right", part = "header") %>% 
  align(i = 1, align = "center", part = "header") %>% 
  set_caption("The number of burials with identification of age and sex at Kiwulan. The NA means no sufficient skeletal remains for determination of age or sex")
ft_age_sex
```
